Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-05-30 TEBenchmarkPaper/article.tex
More detail on aggregation

We can summarise runtimes by choosing their median, as this is more robust than
the mean against long-running outliers, and hence represents performance for a
``typical'' input of that size. Since our methodology measures performance over
many samples, we can also compute the \emph{spread} of our data, for example the
inter-quartile range. This is not possible using the one-off measurements common
in prior evaluation methods.

There are two ways to average the measured precision and (separately) recall for
samples of a particular size. Since these quantities are ratios, their mean
values are known as the \emph{average of the ratios} (AOR), which we can define
for $S$ samples indexed by $1 \leq i \leq S$ as follows:

@@

We interpret these as the \emph{expected} values of precision and recall for
samples of this size, i.e. the expected quality of the \emph{set} of conjectures
that will be generated from such a sample.

The alternative is to calculate \emph{pooled} averages, by combining the
(multi)sets from each sample before taking the ratios. If we multiply the
numerator and denominator by a factor $\frac{1}{S}$ we find that this is
equivalent to using the mean set sizes, hence this is known as the
\emph{ratio of the averages} (ROA):

@@

Larger sets contribute more to a ratio of averages, unlike the mean which treats
each set equally. This weighting gives us expected values of \emph{conjectures}
rather than sets: the ROA for precision is the expected chance of a generated
conjecture being interesting; the ROA for recall is the expected chance that a
ground truth property will be generated. Note that both of these averaging
methods deal with \emph{fractions}: we may also want to know the \emph{absolute}
number of conjectures to expect, which is the mean output size
$\overline{\#\text{generated}}$.

If we instead want to combine precision values \emph{with} recall values (either
individually or pooled) we can calculate their \emph{F-score}, defined as:

>>>>

We can summarise a set of runtimes by choosing the median, as this is more
robust than the mean against long-running outliers, and hence represents
performance for a ``typical'' input of that size. Since our methodology measures
performance over many samples, we can also compute the \emph{spread} of our
data, for example the inter-quartile range. This is not possible using the
one-off measurements common in prior evaluation methods.

Considering precision and recall separately, there are two ways to average these
for a set of samples. Since both of these measurements are ratios, their means
are known as the \emph{average of the ratios} (AOR). Using the definitions of
precision and recall given in $\S$\ref{sec:te}, we can define the average of the
ratios for $S$ samples indexed by $1 \leq i \leq S$ as follows:

@@

We interpret these mean values as the \emph{expected} precision and recall for
samples of this size. In particular, these tell us the quality of the \emph{set}
of conjectures that will be generated if we were to run the tool on such a
sample, but they don't give us direct information about the individual
conjectures themselves. Since these are mean values, they are the reference
point for measures of spread such as the variance, standard deviation and mean
absolute deviation.

The alternative is to calculate \emph{pooled} averages, by combining the
(multi)sets from each sample before taking the ratios. The size of these pooled
sets is simply the sum of the individual set sizes, and ratios of these sums are
equal to ratios of the means (since the normalising factor $\frac{1}{S}$ appears
in both numerator and denominator). Hence these values are known as the
\emph{ratio of the averages} (ROA):

@@

Larger sets contribute more to a ratio of averages, unlike the mean which treats
each set equally. This weighting gives us expected qualities of
\emph{conjectures} rather than sets: the ROA for precision is the expected
chance that some particular generated conjecture will appear in the ground
truth; the ROA for recall is the expected chance that some particular ground
truth property will appear in the generated output.

These averages can differ when there is a large variation in set size. For
example, if we generate a single, interesting conjecture for one sample and 99
uninteresting conjectures for another sample, the AOR (mean) precision will be
$\frac{1}{2}$ but the ROA precision will be $\frac{1}{100}$. This highlights the
importance of knowing \emph{absolute} numbers of conjectures, such as the mean
output size $\overline{\#\text{generated}}$ and its spread, alongside the
proportions given by precision and recall.

It is also possible to combine precision values \emph{with} recall values
(either individually or aggregated) by calculating their \emph{F-score}, defined
as:
